nmds-plots

### 2023-02-20 workflow/notebooks/nmds-plots.Rmd

```{r split_by_outcomes, include=FALSE}
# inner join w sample id column from data/process/cases_full_metadata.csv
# plot will be one per definition, with severe as one color and not severe as other
names(pc)[names(pc) == "group"] <- "sample_id"
pc
combined_df <- pc %>% inner_join( case_data, 
           by=c('sample_id'))
idsa <- combined_df %>% select("axis1", "axis2", "idsa") %>% drop_na(idsa)
attrib <- combined_df %>% select("axis1", "axis2", "attrib") %>% drop_na(attrib)
allcause <- combined_df %>% select("axis1", "axis2", "allcause") %>% drop_na(allcause)

```

```{r plotnmds, echo=FALSE}
data.scores = as.data.frame(idsa)
idsa_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = idsa))
data.scores = as.data.frame(attrib)
attrib_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = attrib))
data.scores = as.data.frame(allcause)
allcause_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = allcause))

idsa_plot
attrib_plot
allcause_plot

```

>>>>

```{r split_by_outcomes, include=FALSE}
# inner join w sample id column from data/process/cases_full_metadata.csv
# plot will be one per definition, with severe as one color and not severe as other
names(pc)[names(pc) == "group"] <- "sample_id"
pc
combined_df <- pc %>% inner_join( case_data, 
           by=c('sample_id'))
idsa <- combined_df %>% select("axis1", "axis2", "idsa") %>% drop_na(idsa) %>% rename(is_severe=idsa) %>% mutate(outcome="IDSA")
attrib <- combined_df %>% select("axis1", "axis2", "attrib") %>% drop_na(attrib) %>% rename(is_severe=attrib) %>% mutate(outcome="Attrib")
allcause <- combined_df %>% select("axis1", "axis2", "allcause") %>% drop_na(allcause) %>% rename(is_severe=allcause) %>% mutate(outcome="Allcause")
all_outcomes <- bind_rows(allcause, attrib, idsa)
```

```{r plotnmds, echo=FALSE}

data.scores = as.data.frame(all_outcomes)

plot <- data.scores %>% ggplot(aes(x=axis1, y=axis2, color = is_severe)) + geom_point(alpha = 0.7) + facet_wrap("outcome", nrow = 1) + theme_bw() + scale_color_manual(values=c(yes="#E41A1C", no="#377EB8"), name="is_severe") + theme(axis.title.x = element_blank(), axis.title.y = element_blank())
plot
```
